The status of PyPy

### 2010-02-08 talk/pycon2010/keynote/talk.tex
I'm sort of happy with slides as they're now.

\begin{frame}
  \frametitle{February 2009}
  \begin{tikzpicture}[remember picture, overlay]
    \node [shift={(1cm, -4cm)}] at (current page.north west) {
      \begin{tikzpicture}[remember picture, overlay, font={\fontsize{8pt}{0pt} \ttfamily}]
        \node [shift={(-1cm, 1.4cm)}, above right] {
          \includegraphics[width=.15\textwidth]{pypy-logo.png}};
        \draw [thick, ->] (1.2cm, 2.5cm) -- (10cm, 2.5cm);
      \end{tikzpicture}
    };
  \end{tikzpicture}
  \begin{itemize}
    \item We merge experiments into mailine PyPy
    \item xxx
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{June 2009}
  \begin{tikzpicture}[remember picture, overlay]
    \node [shift={(1cm, -4cm)}] at (current page.north west) {
      \begin{tikzpicture}[remember picture, overlay, font={\fontsize{8pt}{0pt} \ttfamily}]
        \node [shift={(-1cm, 1.4cm)}, above right] {
          \includegraphics[width=.15\textwidth]{pypy-logo.png}};
        \draw [thick, ->] (1.2cm, 2.5cm) -- (10cm, 2.5cm);
        \draw [fill=blue!20,very thin] (1.7cm, 2.5cm) circle (.06cm);
        \draw (1.7cm, 2.44cm) -- (1.7cm, 2.0cm);
        \draw (1.5cm, 1.5cm) node [rotate=45] {JIT merge};
        \draw [fill=blue!20,very thin] (2.3cm, 2.5cm) circle (.06cm);
        \draw (2.3cm, 2.44cm) -- (2.3cm, 2.0cm);
        \draw (1.95cm, 1.5cm) node [rotate=45] {first example};  
      \end{tikzpicture}
    };
  \end{tikzpicture}
  xxx
\end{frame}

\begin{frame}
  \frametitle{Nice graphs}
\end{frame}

\begin{frame}
  \frametitle{Status}
  \begin{block}{Status of today}
    \begin{itemize}
    \item JIT is fairly good
      \pause
    \item sometimes can consume a lot of memory
      \pause
    \item sometimes keep on compiling all the time
      \pause
    \item GCs are pretty good
      \pause
    \item VMs algorithms are not as polished as CPython
      ones [xxx reword]
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{Near future}
  \begin{itemize}
    \item release March 2010
      \pause
    \item first PyPy release to contain JIT!
    \item mostly to try it out
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{February 2009}
  \begin{tikzpicture}[remember picture, overlay]
    \node [shift={(1cm, -4cm)}] at (current page.north west) {
      \begin{tikzpicture}[remember picture, overlay, font={\fontsize{8pt}{0pt} \ttfamily}]
        \node [shift={(-1cm, 1.4cm)}, above right] {
          \includegraphics[width=.15\textwidth]{pypy-logo.png}};
        \draw [thick, ->] (1.2cm, 2.5cm) -- (10cm, 2.5cm);
      \end{tikzpicture}
    };
  \end{tikzpicture}
  \begin{itemize}
    \item we merge experiments into mailine PyPy
    \item xxx
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{September 2009}
  \begin{tikzpicture}[remember picture, overlay]
    \node [shift={(1cm, -4cm)}] at (current page.north west) {
      \begin{tikzpicture}[remember picture, overlay, font={\fontsize{8pt}{0pt} \ttfamily}]
        \node [shift={(-1cm, 1.4cm)}, above right] {
          \includegraphics[width=.15\textwidth]{pypy-logo.png}};
        \draw [thick, ->] (1.2cm, 2.5cm) -- (10cm, 2.5cm);
        \draw [fill=blue!20,very thin] (1.7cm, 2.5cm) circle (.06cm);
        \draw (1.7cm, 2.44cm) -- (1.7cm, 2.0cm);
        \draw (1.5cm, 1.5cm) node [rotate=45] {JIT merge};
        \draw [fill=blue!20,very thin] (4.3cm, 2.5cm) circle (.06cm);
        \draw (4.3cm, 2.44cm) -- (4.3cm, 2.0cm);
        \draw (3.95cm, 1.5cm) node [rotate=45] {first example};  
      \end{tikzpicture}
    };
  \end{tikzpicture}
  \begin{itemize}
    \item we manage to speed first non-trivial benchmark
    \item richards - a simple, object oriented code
    \item a variety of optimizations involved
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{February 2010 - now}
  \begin{tikzpicture}[remember picture, overlay]
    \node [shift={(1cm, -4cm)}] at (current page.north west) {
      \begin{tikzpicture}[remember picture, overlay, font={\fontsize{8pt}{0pt} \ttfamily}]
        \node [shift={(-1cm, 1.4cm)}, above right] {
          \includegraphics[width=.15\textwidth]{pypy-logo.png}};
        \draw [thick, ->] (1.2cm, 2.5cm) -- (10cm, 2.5cm);
        \draw [fill=blue!20,very thin] (1.7cm, 2.5cm) circle (.06cm);
        \draw (1.7cm, 2.44cm) -- (1.7cm, 2.0cm);
        \draw (1.5cm, 1.5cm) node [rotate=45] {JIT merge};
        \draw [fill=blue!20,very thin] (4.3cm, 2.5cm) circle (.06cm);
        \draw (4.3cm, 2.44cm) -- (4.3cm, 2.0cm);
        \draw (3.95cm, 1.5cm) node [rotate=45] {first example};  
        \draw [fill=blue!20,very thin] (7.3cm, 2.5cm) circle (.06cm);
        \draw (7.3cm, 2.44cm) -- (7.3cm, 2.0cm);
        \draw (6.95cm, 1.5cm) node [rotate=45] {richards};  
      \end{tikzpicture}
    };
  \end{tikzpicture}
  We run a variety of benchmarks nightly.
\end{frame}

\begin{frame}
  \frametitle{Status}
  \begin{block}{Status of today}
    \begin{itemize}
    \item JIT is fairly good
      \pause
    \item can consume a lot of memory
      \pause
    \item can recompile code too many times
      \pause
    \item GCs are pretty good
      \pause
    \item runtime algorithms are not as polished as CPython
      ones (ie strings, regexes)
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{Near future}
  \begin{itemize}
    \item release March 2010
      \pause
    \item first PyPy release to contain JIT!
    \item mostly to try it out
      \pause
    \item we just got a bit more {\bf EU funding}
    \item we're actively looking for {\bf sponsoring} to continue PyPy development
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Come to my next talk!}
  \begin{block}{speed of PyPy}
    ... or how to write programs that play well with the JIT
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{That's all}
  Thank you for your attention
  \begin{itemize}
    \item http://morepypy.blogspot.com
    \item http://pypy.org
    \item http://merlinux.de
    \item these slides are already online
  \end{itemize}
\end{frame}
